New lower bounds for Schur and weak Schur numbers

### 2021-04-09 article/article.tex

\par
The fourth section gives new insight on the method that was formerly used to achieve new lower bounds. The principle behind it
might have discarded many interesting partititions of the search space and lowered the highest value that can be reached within it.
However, algorithms based on randomness such as Monte-Carlo algorithms may appear very useful if used in a search space with more
potential. For example, such an algorithm could be used to find better templates and improve inequalities and lower bounds for high values
of \(n\). This could be the subject fo a future work. Nevertheless, it would not help for the smallest values.

>>>>

\par
The fourth section gives new insight on the method that was formerly used to achieve new lower bounds for weak Schur numbers. The principle behind it
might have discarded many interesting partitions of the search space and lowered the highest value that can be reached within it.
However, algorithms based on randomness such as Monte-Carlo algorithms may appear very useful if used in a search space with more
potential. For example, such an algorithm could be used to find better templates and improve inequalities and lower bounds for high values
of \(n\). This could be the subject fo a future work. Nevertheless, it would not help for the smallest values.

### 2021-04-09 article/schur.tex

\begin{center}
\(\overset{S^+(3)}{\left. \overleftrightarrow{\begin{tabular}{|*{9}{c|}}
	\hline
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
	\hline
	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & \cellcolor{yellow} 15 & \cellcolor{red} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
	\hline
	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & \cellcolor{yellow} 24 & \cellcolor{red} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
	\hline
	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{blue} 32 & \cellcolor{blue} 33 & \cellcolor{red} 34 & \cellcolor{blue} 35 & \cellcolor{blue} 36\\
	\hline
	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 & & & & &\\
	\hline
\end{tabular}}
\right \updownarrow S(2)}\)
\end{center}

\begin{center}
\(S^+(3)\)\\
\begin{tabular}{|*{9}{c|}}
	\hline 
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
	\hline
\end{tabular} \\

\(S(2)\) \\
\begin{tabular}{|*{4}{c|}}
	\hline 
	\cellcolor{blue} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{blue} 4 \\
	\hline
\end{tabular}
\end{center}

To compare, here is a classic Abbott and Hanson partition : \(S(2+2) \geqslant S(2)(2S(2)+1)+S(2) \). \\

\begin{center}
\begin{tabular}{|*{9}{c|}}
	\hline
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{blue} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
	\hline
	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & \cellcolor{yellow} 15 & \cellcolor{yellow} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
	\hline
	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & \cellcolor{yellow} 24 & \cellcolor{yellow} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
	\hline
	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{blue} 32 & \cellcolor{blue} 33 & \cellcolor{blue} 34 & \cellcolor{blue} 35 & \cellcolor{blue} 36 \\
	\hline
	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 & & & & &\\
	\hline
\end{tabular}
\end{center}

@@

We now define \(h : [\![1,pq+m_{k+1}-1]\!] \longrightarrow [\![1,n+k]\!] \) as follows :
\( \forall x \in [\![1,pq + m_{k+1}-1]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q+1]\!] \) and \( u \in
[\![0,p-1]\!] \).
This decomposition if of course unique. \\
If \(f(p-u) \leqslant k\), we set \(h(x) = f(p-u)\), else (i.e \(f(p-u) = k + 1)\) \(h(x) = k + g(\alpha) \). \\
If \(\alpha = q+1\), we have a problem plugging it into \(g\). Hopefully, this issue never arises : if 
\(\alpha = q+1\), we have \(u > p - m_{k+1}\) since \(x \in [\![1,pq + m_{k+1}-1]\!]\), hence \(p-u < m_{k+1}\) and \(f(p-u) \leqslant k\). \\
Prooving that the partition of \([\![1,pq]\!]\) induced by \(h\) is sum-free will complete the proof.

Let \(x,y \in [\![1,pq + m_{k+1}-1]\!]\), with \(h(x) = h(y)\) and \(x+y \leqslant pq+m_{k+1}-1\). We write \(x = \alpha p - u\) and \(y =
\beta p - v\). \\
We simply need \(h(x+y) \neq h(x)\). \\

>>>>

\begin{center}
\[
\begin{array}{|*{9}{c|}}
	\multicolumn{9}{c}{\overset{S^+(3)}{\overbrace{\rule{6cm}{0pt}}}} \\
	\hline
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9 \\
	\hline
	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & \cellcolor{yellow} 15 & \cellcolor{red} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
	\hline
	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & \cellcolor{yellow} 24 & \cellcolor{red} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
	\hline
	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{blue} 32 & \cellcolor{blue} 33 & \cellcolor{red} 34 & \cellcolor{blue} 35 & \cellcolor{blue} 36\\
	\hline
	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 \\
	\cline{1-4}
\end{array}
\]
\end{center}

\begin{center}
\[
S^+(3) 
\begin{array}{|*{9}{c|}}
	\hline 
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
	\hline
\end{array}  \]
\[
S(2) 
\begin{array}{|*{4}{c|}}
	\hline 
	\cellcolor{blue} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{blue} 4 \\
	\hline
\end{array}
\]
\end{center}

To compare, here is a classic Abbott and Hanson partition : \(S(2+2) \geqslant S(2)(2S(2)+1)+S(2) \). 
\begin{center}
\[
\begin{array}{|*{9}{c|}}
	\multicolumn{4}{c}{\overset{S(2)}{\overbrace{\rule{2.6cm}{0pt}}}} \\
	\hline
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{blue} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
	\hline
	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & \cellcolor{yellow} 15 & \cellcolor{yellow} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
	\hline
	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & \cellcolor{yellow} 24 & \cellcolor{yellow} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
	\hline
	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{blue} 32 & \cellcolor{blue} 33 & \cellcolor{blue} 34 & \cellcolor{blue} 35 & \cellcolor{blue} 36 \\
	\hline
	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 \\
	\cline{1-4}
\end{array}
\]
\end{center}

@@

We now define \(h : [\![1,pq+m_{k+1}-1]\!] \longrightarrow [\![1,n+k]\!] \) as follows :
\( \forall x \in [\![1,pq + m_{k+1}-1]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q+1]\!] \) and \( u \in
[\![0,p-1]\!] \).
This decomposition if of course unique. \\

If \(f(p-u) \leqslant k\), we set \(h(x) = f(p-u)\), else (i.e \(f(p-u) = k + 1)\) \(h(x) = k + g(\alpha) \). \\
If \(\alpha = q+1\), we have a problem plugging it into \(g\). Hopefully, this issue never arises : if 
\(\alpha = q+1\), we have \(u > p - m_{k+1}\) since \(x \in [\![1,pq + m_{k+1}-1]\!]\), hence \(p-u < m_{k+1}\) and \(f(p-u) \leqslant k\). \\

Prooving that the partition of \([\![1,pq]\!]\) induced by \(h\) is sum-free will complete the proof.\\

Let \(x,y \in [\![1,pq + m_{k+1}-1]\!]\), with \(h(x) = h(y)\) and \(x+y \leqslant pq+m_{k+1}-1\). We write \(x = \alpha p - u\) and \(y =
\beta p - v\). We simply need \(h(x+y) \neq h(x)\). \\
